---
title: "Figure 6. FOS and SCFAs reduced LD-induced cholesterol gallstones"
author: "Ye Liu"
date: "2024/1/20"
format: html
---

a\. Relative abundance of the discriminatory microbial genes

```{r}
#| echo: false
#| eval: true
#| results: markup
#| warning: false
#| message: false
#| fig-show: hold
#| fig.width: 1.6
#| fig.height: 2.1
#| out.width: "100%"
library(limma)
library(reshape2)
library(ggpubr)
library(dplyr)

geneFile="gene.txt"        
cliFile="1.group_m.txt"             

data<-read.csv("sig_gene.csv",header = T)
df <- read.csv("very_easy_input.csv")
diff<- data[data$Species %in% df$name, ]
#write.csv(diff,"pathway_scfas_ko gene.csv")

data<-read.csv("pathway_scfas_ko gene.csv",header = T)
data1<-as.data.frame(t(data))
colnames(data1)<-data$Species
data1<-data1[-1,]
data1$group<- factor(data1$group,levels = c("Health","Disease"))

library(reshape2)
data1_melted <- melt(data1, id.vars = "group", variable.name = "Gene", value.name = "Abundance")
group_means <- data1_melted %>%
  mutate(Abundance = as.numeric(Abundance)) %>%
  group_by(group,Gene) %>%
  summarize(mean_Abundance = mean(Abundance))
group_means$value<-10000*group_means$mean_Abundance

group_means <- group_means[!group_means$Gene %in% c("OXCT","PCCA,pccA"), ]

pdf("fig6a.pdf",
    width = 1.6,height =2.1)
p <- ggplot(group_means , aes(x = Gene, y = value, fill = group)) +
  geom_bar(position = position_dodge(0.9), stat = "summary", fun = "mean", color = NA) +
  geom_errorbar(position = position_dodge(0.9), stat = "summary", fun.data = mean_se, width = 0.2,aes(color = factor(group))) +
  theme_classic() +
  xlab("")+labs(y="Value")+
  theme(legend.position="none",
        panel.grid = element_line(color = 'gray', linetype = 0, size = 0.2),
        panel.background = element_blank(), 
        axis.title.x = element_text(size = 7,face = "bold"),
        axis.title.y = element_text(size = 7,face = "bold"),
        axis.text.x = element_text(size = 6.5),
        axis.text.y = element_text(size = 6.5),
        axis.ticks.x=element_line(color="black",size=0.5,lineend = 1),
        axis.ticks.y=element_line(color="black",size=0.5,lineend = 1),
        legend.text=element_text(size=0.2),legend.key.size= unit(0.1, "cm"),  
        legend.title=element_blank(),
        plot.margin =unit(c(0.05,0.05,0.05,0.05), "cm"))+ coord_cartesian(ylim = c(0, 4))
p1 <- p + scale_fill_manual(values = c("#759884","#1972B6"))
p2=p1+scale_y_continuous(breaks = c(0,1,2,3,4),expand=c(0,0))+expand_limits(y=c(0,4))+
  scale_color_manual(values = c("#759884","#1972B6"))
p3<-p2+coord_flip()
p3
dev.off()

p3

```

e-m: Box plot

\(E\) The relative lipid content of each group. (F) The grade of experimental cholesterol gallstones (CGSs) in the mice was based on the observed gallstone. (G) The ratio of liver weight to body weight in different groups. (H) Level of serum glucose. Each box centres on the median, with lower and upper bounds representing the first and third quartiles (25th and 75th percentile), respectively (*n* = 12). (I−M) Levels of serum ALT, AST, TC, TG, and TBA.

TC, total cholesterol; TG, triglycerides; ALT, alanine aminotransferase; AST, aspartate aminotransferase; TBA, total bile acid; NaB, sodium butyrate; NaP, sodium propionate; NaA, sodium acetate; FOS, fructooligosaccharide; SCFAs, short-chain fatty acids. *p*-values were calculated using one-way ANOVA with Dunnett’s post hoc test.

```{r}
#| echo: false
#| eval: true
#| results: markup
#| warning: false
#| message: false
#| fig-show: hold
#| fig.width: 1.1
#| fig.height: 1.5
#| out.width: "100%"
library(reshape2)
library(ggplot2)
library(randomcoloR)
library(ggsci)
library(ggplot2)
library(gridExtra)
library(showtext)
library(readxl)

cli3 <- read_xlsx("rel_lipid_oil.xlsx", 3)

cli3$Group<-factor(cli3$Group,levels = c("LD","NaB","NaP","NaA","FOS"))

# Shapiro-Wilk normality test for each group
#by(cli3$`Relative Area of Lipid Droplets`, cli3$Group, shapiro.test)

#aov_result <- aov(`Relative Area of Lipid Droplets` ~ Group, data = cli3)
# 2. 使用 Dunnett's t-test 进行事后比较
#library(multcomp)
#dunnett_result <- glht(aov_result, linfct = mcp(Group = "Dunnett"))
# 查看 Dunnett 检验的结果
#summary(dunnett_result)

pdf("Lipid.pdf",
    width = 1.1,height = 1.5)
p <- ggplot(cli3, aes(x = Group, y = `Relative Area of Lipid Droplets`, fill = factor(Group))) +
  geom_violin(aes(fill = Group), position = position_dodge(0.9),alpha = 0.9 ,width = 1.0,linetype = "blank") +
  geom_boxplot(aes(fill=Group),position = position_dodge(0.9),lwd=0.1,width = 0.3,outlier.shape = NA)+
  theme_classic() +
  xlab("") +
  labs(y = "Relative Area of Lipid Droplets") +
  theme(legend.position = "none",
        panel.grid = element_line(color = 'gray', linetype = 0, size = 0.2),
        panel.background = element_blank(), 
        axis.title.x = element_text(size = 8, face = "bold"),
        axis.title.y = element_text(size = 8, face = "bold"),
        axis.text.x = element_text(size = 8, , angle = 45, hjust = 1),
        axis.text.y = element_text(size = 8),
        axis.ticks.x = element_line(color = "black", size = 1, lineend = 1),
        axis.ticks.y = element_line(color = "black", size = 1, lineend = 1),
        legend.text = element_text(size = 9),
        legend.title = element_blank(),
        plot.margin =unit(c(0.5,0.1,0.05,0.1), "cm"))
p1 <- p + scale_fill_manual(values = c("#B2B9C1","#35395A","#E4B6B4","#C0C880","#5C9591")) 

p2=p1+scale_y_continuous(breaks = c(0, 0.5, 1.0, 1.5,2.0),expand=c(0,0))+expand_limits(y=c(0,2.0))
p2
dev.off()

p2


cli1 <- read_xlsx("1.biochemical.xlsx",2)

cli1$Group<-factor(cli1$Group,levels = c("LD","NaB","NaP","NaA","FOS"))


# 2. 使用 Dunnett's t-test 进行事后比较
library(multcomp)
#dunnett_result <- glht(aov_result, linfct = mcp(Group = "Dunnett"))
# 查看 Dunnett 检验的结果
#summary(dunnett_result)

pdf("Liver weight_Body weight.pdf",
    width = 1.1,height = 1.4)
p<-ggplot(cli1, aes(x = Group, y = `liver/body`, fill = factor(Group))) +
  geom_bar(position = position_dodge(0.9), stat = "summary", fun = "mean", color = NA) +
  geom_errorbar(position = position_dodge(0.9), stat = "summary", fun.data = mean_se, width = 0.2,aes(color = factor(Group))) +
  #geom_point(aes(fill=Group),position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.9), shape = factor(Group),color = "black", size = 0.6) + # 设置散点颜色为白色，边的颜色与group颜色对应，形状不同
  geom_jitter(color=cli1$col,fill=NA,width =0.2,shape =cli1$Group, size = 0.65)+
  theme_classic() +
  xlab("")+labs(y="Liver weight/Body weight")+
  theme(legend.position="none",
        panel.grid = element_line(color = 'gray', linetype = 0, size = 0.2), 
        panel.background = element_blank(), 
        axis.title.x = element_text(size = 10,face = "bold"),
        axis.title.y = element_text(size = 7,face = "bold"),
        axis.text.x = element_text(size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 8),
        axis.ticks.x=element_line(color="black",size=0.5,lineend = 1),
        axis.ticks.y=element_line(color="black",size=0.5,lineend = 1),
        legend.text=element_text(size=9),
        legend.title=element_blank(),
        plot.margin =unit(c(0.05,0,0,0), "cm"))
p1 <- p + scale_fill_manual(values = c("#B2B9C1","#35395A","#E4B6B4","#C0C880","#5C9591"))
p2=p1+scale_y_continuous(breaks = c(0, 0.02, 0.04, 0.06,0.08),expand=c(0,0))+expand_limits(y=c(0,0.10))+
  scale_color_manual(values =  c("#B2B9C1","#35395A","#E4B6B4","#C0C880","#5C9591"))
p2
dev.off()

p2

pdf("TC.pdf",
    width = 0.9,height = 1.4)
p<-ggplot(cli1, aes(x = Group, y = TC, fill = factor(Group))) +
  geom_bar(position = position_dodge(0.9), stat = "summary", fun = "mean", color = NA) +
  geom_errorbar(position = position_dodge(0.9), stat = "summary", fun.data = mean_se, width = 0.2,aes(color = factor(Group))) +
  #geom_point(aes(fill=Group),position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.9), shape = factor(Group),color = "black", size = 0.6) + # 设置散点颜色为白色，边的颜色与group颜色对应，形状不同
  geom_jitter(color=cli1$col,fill=NA,width =0.2,shape =cli1$Group, size = 0.65)+
  theme_classic() +
  xlab("")+labs(y="Serum TC")+
  theme(legend.position="none",
        panel.grid = element_line(color = 'gray', linetype = 0, size = 0.2), 
        panel.background = element_blank(), 
        axis.title.x = element_text(size = 10,face = "bold"),
        axis.title.y = element_text(size = 7,face = "bold"),
        axis.text.x = element_text(size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 8),
        axis.ticks.x=element_line(color="black",size=0.5,lineend = 1),
        axis.ticks.y=element_line(color="black",size=0.5,lineend = 1),
        legend.text=element_text(size=9),
        legend.title=element_blank(),
        plot.margin =unit(c(0.05,0,0,0), "cm"))
p1 <- p + scale_fill_manual(values = c("#B2B9C1","#35395A","#E4B6B4","#C0C880","#5C9591"))
p2=p1+scale_y_continuous(breaks = c(0, 2, 4, 6,8),expand=c(0,0))+expand_limits(y=c(0,8))+
  scale_color_manual(values = c("#B2B9C1","#35395A","#E4B6B4","#C0C880","#5C9591"))
p2
dev.off()
p2

pdf("TG.pdf",
    width = 1.0,height = 1.4)
p<-ggplot(cli1, aes(x = Group, y = TG, fill = factor(Group))) +
  geom_bar(position = position_dodge(0.9), stat = "summary", fun = "mean", color = NA) +
  geom_errorbar(position = position_dodge(0.9), stat = "summary", fun.data = mean_se, width = 0.2,aes(color = factor(Group))) +
  #geom_point(aes(fill=Group),position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.9), shape = factor(Group),color = "black", size = 0.6) + # 设置散点颜色为白色，边的颜色与group颜色对应，形状不同
  geom_jitter(color=cli1$col,fill=NA,width =0.2,shape =cli1$Group, size = 0.65)+
  theme_classic() +
  xlab("")+labs(y="Serum TG")+
  theme(legend.position="none",
        panel.grid = element_line(color = 'gray', linetype = 0, size = 0.2), 
        panel.background = element_blank(), 
        axis.title.x = element_text(size = 10,face = "bold"),
        axis.title.y = element_text(size = 7,face = "bold"),
        axis.text.x = element_text(size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 8),
        axis.ticks.x=element_line(color="black",size=0.5,lineend = 1),
        axis.ticks.y=element_line(color="black",size=0.5,lineend = 1),
        legend.text=element_text(size=9),
        legend.title=element_blank(),
        plot.margin =unit(c(0.05,0,0,0), "cm"))+ coord_cartesian(ylim = c(0, 0.6))
p1 <- p + scale_fill_manual(values = c("#B2B9C1","#35395A","#E4B6B4","#C0C880","#5C9591"))
p2=p1+scale_y_continuous(breaks = c(0, 0.2,0.4, 0.6),expand=c(0,0))+expand_limits(y=c(0,0.6))+
  scale_color_manual(values = c("#B2B9C1","#35395A","#E4B6B4","#C0C880","#5C9591"))
p2
dev.off()
p2

pdf("TBA.pdf",
    width = 1.0,height = 1.4)
p<-ggplot(cli1, aes(x = Group, y = TBA, fill = factor(Group))) +
  geom_bar(position = position_dodge(0.9), stat = "summary", fun = "mean", color = NA) +
  geom_errorbar(position = position_dodge(0.9), stat = "summary", fun.data = mean_se, width = 0.2,aes(color = factor(Group))) +
  #geom_point(aes(fill=Group),position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.9), shape = factor(Group),color = "black", size = 0.6) + # 设置散点颜色为白色，边的颜色与group颜色对应，形状不同
  geom_jitter(color=cli1$col,fill=NA,width =0.2,shape =cli1$Group, size = 0.65)+
  theme_classic() +
  xlab("")+labs(y="Serum TBA (umol/L)")+
  theme(legend.position="none",
        panel.grid = element_line(color = 'gray', linetype = 0, size = 0.2), 
        panel.background = element_blank(), 
        axis.title.x = element_text(size = 10,face = "bold"),
        axis.title.y = element_text(size = 7,face = "bold"),
        axis.text.x = element_text(size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 8),
        axis.ticks.x=element_line(color="black",size=0.5,lineend = 1),
        axis.ticks.y=element_line(color="black",size=0.5,lineend = 1),
        legend.text=element_text(size=9),
        legend.title=element_blank(),
        plot.margin =unit(c(0.05,0,0,0), "cm"))+ coord_cartesian(ylim = c(0, 160))
p1 <- p + scale_fill_manual(values = c("#B2B9C1","#35395A","#E4B6B4","#C0C880","#5C9591"))
p2=p1+scale_y_continuous(breaks = c(0, 40,80, 120,160),expand=c(0,0))+expand_limits(y=c(0,160))+
  scale_color_manual(values = c("#B2B9C1","#35395A","#E4B6B4","#C0C880","#5C9591"))
p2
dev.off()
p2

pdf("ALT.pdf",
    width = 1.0,height = 1.4)
p<-ggplot(cli1, aes(x = Group, y = ALT, fill = factor(Group))) +
  geom_bar(position = position_dodge(0.9), stat = "summary", fun = "mean", color = NA) +
  geom_errorbar(position = position_dodge(0.9), stat = "summary", fun.data = mean_se, width = 0.2,aes(color = factor(Group))) +
  #geom_point(aes(fill=Group),position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.9), shape = factor(Group),color = "black", size = 0.6) + # 设置散点颜色为白色，边的颜色与group颜色对应，形状不同
  geom_jitter(color=cli1$col,fill=NA,width =0.2,shape =cli1$Group, size = 0.65)+
  theme_classic() +
  xlab("")+labs(y="Serum ALT (U/L)")+
  theme(legend.position="none",
        panel.grid = element_line(color = 'gray', linetype = 0, size = 0.2), 
        panel.background = element_blank(), 
        axis.title.x = element_text(size = 10,face = "bold"),
        axis.title.y = element_text(size = 7,face = "bold"),
        axis.text.x = element_text(size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 8),
        axis.ticks.x=element_line(color="black",size=0.5,lineend = 1),
        axis.ticks.y=element_line(color="black",size=0.5,lineend = 1),
        legend.text=element_text(size=9),
        legend.title=element_blank(),
        plot.margin =unit(c(0.05,0,0,0), "cm"))+ coord_cartesian(ylim = c(0, 800))
p1 <- p + scale_fill_manual(values = c("#B2B9C1","#35395A","#E4B6B4","#C0C880","#5C9591"))
p2=p1+scale_y_continuous(breaks = c(0, 250,500, 750),expand=c(0,0))+expand_limits(y=c(0,800))+
  scale_color_manual(values = c("#B2B9C1","#35395A","#E4B6B4","#C0C880","#5C9591"))
p2
dev.off()

p2
pdf("AST.pdf",
    width = 1.0,height = 1.4)
p<-ggplot(cli1, aes(x = Group, y = AST, fill = factor(Group))) +
  geom_bar(position = position_dodge(0.9), stat = "summary", fun = "mean", color = NA) +
  geom_errorbar(position = position_dodge(0.9), stat = "summary", fun.data = mean_se, width = 0.2,aes(color = factor(Group))) +
  #geom_point(aes(fill=Group),position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.9), shape = factor(Group),color = "black", size = 0.6) + # 设置散点颜色为白色，边的颜色与group颜色对应，形状不同
  geom_jitter(color=cli1$col,fill=NA,width =0.2,shape =cli1$Group, size = 0.65)+
  theme_classic() +
  xlab("")+labs(y="Serum AST (U/L)")+
  theme(legend.position="none",
        panel.grid = element_line(color = 'gray', linetype = 0, size = 0.2), 
        panel.background = element_blank(), 
        axis.title.x = element_text(size = 10,face = "bold"),
        axis.title.y = element_text(size = 7,face = "bold"),
        axis.text.x = element_text(size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 8),
        axis.ticks.x=element_line(color="black",size=0.5,lineend = 1),
        axis.ticks.y=element_line(color="black",size=0.5,lineend = 1),
        legend.text=element_text(size=9),
        legend.title=element_blank(),
        plot.margin =unit(c(0.05,0,0,0), "cm"))+ coord_cartesian(ylim = c(0, 800))
p1 <- p + scale_fill_manual(values = c("#B2B9C1","#35395A","#E4B6B4","#C0C880","#5C9591"))
p2=p1+scale_y_continuous(breaks = c(0, 200,400,600,800),expand=c(0,0))+expand_limits(y=c(0,800))+
  scale_color_manual(values = c("#B2B9C1","#35395A","#E4B6B4","#C0C880","#5C9591"))
p2
dev.off()
p2
pdf("glu.pdf",
    width = 1.0,height = 1.4)
p<-ggplot(cli1, aes(x = Group, y =`GLU-Q`, fill = factor(Group))) +
  geom_bar(position = position_dodge(0.9), stat = "summary", fun = "mean", color = NA) +
  geom_errorbar(position = position_dodge(0.9), stat = "summary", fun.data = mean_se, width = 0.2,aes(color = factor(Group))) +
  #geom_point(aes(fill=Group),position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.9), shape = factor(Group),color = "black", size = 0.6) + # 设置散点颜色为白色，边的颜色与group颜色对应，形状不同
  geom_jitter(color=cli1$col,fill=NA,width =0.2,shape =cli1$Group, size = 0.65)+
  theme_classic() +
  xlab("")+labs(y="Serum glucose (mmol/L)")+
  theme(legend.position="none",
        panel.grid = element_line(color = 'gray', linetype = 0, size = 0.2), 
        panel.background = element_blank(), 
        axis.title.x = element_text(size = 10,face = "bold"),
        axis.title.y = element_text(size = 7,face = "bold"),
        axis.text.x = element_text(size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 8),
        axis.ticks.x=element_line(color="black",size=0.5,lineend = 1),
        axis.ticks.y=element_line(color="black",size=0.5,lineend = 1),
        legend.text=element_text(size=9),
        legend.title=element_blank(),
        plot.margin =unit(c(0.05,0,0,0), "cm"))+ coord_cartesian(ylim = c(0, 12))
p1 <- p + scale_fill_manual(values = c("#B2B9C1","#35395A","#E4B6B4","#C0C880","#5C9591"))+
  scale_color_manual(values =c("#B2B9C1","#35395A","#E4B6B4","#C0C880","#5C9591"))
p2
dev.off()

p2

pdf("grade.pdf",
    width = 1.3,height = 1.6)
p<-ggplot(cli1, aes(x = Group, y = grade, fill = factor(Group))) +
  geom_bar(position = position_dodge(0.9), stat = "summary", fun = "mean", color = NA) +
  geom_errorbar(position = position_dodge(0.9), stat = "summary", fun.data = mean_se, width = 0.2,aes(color = factor(Group))) +
  geom_jitter(color=cli1$col,fill=NA,width =0.2,shape =cli1$Group, size = 0.65)+
  theme_classic() +
  xlab("")+labs(y="Grade")+
  theme(legend.position="none",
        panel.grid = element_line(color = 'gray', linetype = 0, size = 0.2),
        panel.background = element_blank(), 
        axis.title.x = element_text(size = 10,face = "bold"),
        axis.title.y = element_text(size = 8,face = "bold"),
        axis.text.x = element_text(size = 7, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 7),
        axis.ticks.x=element_line(color="black",size=0.5,lineend = 1),
        axis.ticks.y=element_line(color="black",size=0.5,lineend = 1),
        legend.text=element_text(size=9),
        legend.title=element_blank(),
        plot.margin =unit(c(0.05,0,0,0), "cm"))
p1 <- p + scale_fill_manual(values = c("#B2B9C1","#35395A","#E4B6B4","#C0C880","#BFAC93"))
p2=p1+scale_y_continuous(breaks = c(0, 2, 4, 6),expand=c(0,0))+expand_limits(y=c(0,6))+
  scale_color_manual(values = c("#B2B9C1","#35395A","#E4B6B4","#C0C880","#BFAC93"))
p2
dev.off()

p2
```
